Climate change projected to reduce European life expectancy \thanks{All data and code that supports these conclusions are available as supplementary materials.}

### 2018-05-14 MS-cclifeexpec.Rmd
duplicate figures removed.

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: xelatex
    template: LATEX/svm-latex-ms.tex
title: "Climate change projected to reduce European life expectancy"
thanks: "All data and code that supports these conclusions are available as supplementary materials."
author:
# - name: Mathew E. Hauer^1^*
#   affiliation: University of Georgia
# - name: Alexis R. Santos^2^
#   affiliation: Pennsylvania State University

@@

<!-- * Corresponding author. hauer@uga.edu. p: 706-542-9369. -->

<!-- ^1^ Carl Vinson Institute of Government, University of Georgia. 201 N. Milledge Ave. Athens, GA USA 30602. -->

<!-- ^2^ Department of Sociology and Criminology, Pennsylvania State University. 901 Oswald Tower, University Park, PA USA 16802. -->

@@

```{r echo = FALSE, fig.cap=paste("Change in life expectancy at birth ($e_0$) due to business-as-usual climate change. We report changes in life expectancies due to climate change for twenty-eight European countries. The central values represent the ensemble median while the stems represent the upper and lower bounds of the inter-model climate variability.")}

@@

```{r echo = FALSE, warning= FALSE, message = FALSE, fig.cap=paste("Estimated reduction in life expectancy at birth ($e_0$) by the 2080s under the $MID$ scenario.")}

>>>>

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: xelatex
    template: LATEX/svm-latex-ms.tex
title: "Climate change projected to reduce European life expectancy"
thanks: "All data and code that supports these conclusions are available as supplementary materials."
author:
- name: Mathew E. Hauer^1^*
  affiliation: University of Georgia
- name: Alexis R. Santos^2^
  affiliation: Pennsylvania State University

@@

* Corresponding author. hauer@uga.edu. p: 706-542-9369.

^1^ Carl Vinson Institute of Government, University of Georgia. 201 N. Milledge Ave. Athens, GA USA 30602.

^2^ Department of Sociology and Criminology, Pennsylvania State University. 901 Oswald Tower, University Park, PA USA 16802.

@@

@@

### 2018-05-14 MS-cclifeexpec.tex
duplicate figures removed.

\author{}

@@

\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
             pdfkeywords = {Climate change, Life expectancy, Mortality, Demography, Excess
mortality, Europe, Public health},  
            pdftitle={Climate change projected to reduce European life expectancy},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

{
   \vskip 13.5pt\relax \normalsize\fontsize{11}{12}

@@

\noindent \doublespacing \newpage

@@

\begin{figure}
\centering
\includegraphics{MS-cclifeexpec_files/figure-latex/unnamed-chunk-2-1.pdf}
\caption{Change in life expectancy at birth (\(e_0\)) due to
business-as-usual climate change. We report changes in life expectancies
due to climate change for twenty-eight European countries. The central
values represent the ensemble median while the stems represent the upper
and lower bounds of the inter-model climate variability.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{MS-cclifeexpec_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{Estimated reduction in life expectancy at birth (\(e_0\)) by
the 2080s under the \(MID\) scenario.}
\end{figure}

>>>>

\author{\Large Mathew E. Hauer\textsuperscript{1}*\vspace{0.05in} \newline\normalsize\emph{University of Georgia}   \and \Large Alexis R. Santos\textsuperscript{2}\vspace{0.05in} \newline\normalsize\emph{Pennsylvania State University}  }

@@

\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Mathew E. Hauer\textsuperscript{1}* (University of Georgia) and Alexis R. Santos\textsuperscript{2} (Pennsylvania State University)},
             pdfkeywords = {Climate change, Life expectancy, Mortality, Demography, Excess
mortality, Europe, Public health},  
            pdftitle={Climate change projected to reduce European life expectancy},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

{
   \vskip 13.5pt\relax \normalsize\fontsize{11}{12} 
\textbf{\authorfont Mathew E. Hauer\textsuperscript{1}*} \hskip 15pt \emph{\small University of Georgia}   \par \textbf{\authorfont Alexis R. Santos\textsuperscript{2}} \hskip 15pt \emph{\small Pennsylvania State University}

@@

\noindent \doublespacing \begin{itemize}
\tightlist
\item
  Corresponding author.
  \href{mailto:hauer@uga.edu}{\nolinkurl{hauer@uga.edu}}. p:
  706-542-9369.
\end{itemize}

\textsuperscript{1} Carl Vinson Institute of Government, University of
Georgia. 201 N. Milledge Ave. Athens, GA USA 30602.

\textsuperscript{2} Department of Sociology and Criminology,
Pennsylvania State University. 901 Oswald Tower, University Park, PA USA
16802.

@@

@@
